Improving cropland maps through tight integration of human and machine intelligence

### 2020-08-19 inst/manuscript/manuscript.Rmd
Reorganize into new scripts several of the pre-processing scripts

## Ghana's croplands
- Average field size
- Cropland percentage
- Comparison against other products (croplands.org; Sentinel Landcover)

>>>>

## Ghana's croplands
Two separate maps of cropland were produced for each AOI, one derived from the cropland probability map, and the other from the segmented field boundaries.

- Average field size
- Cropland percentage
- Comparison against other products (croplands.org; Sentinel Landcover)
